Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-27 analysis/paper_draft4.Rmd
updated paper to use revised figures

load_path <- here::here("figures","SD_sensitivity.jpg")
knitr::include_graphics(load_path)

@@

load_path <- here::here("figures","compatibility_plot.jpg")
knitr::include_graphics(load_path)

@@

load_path <- here::here("figures","simultaneous_sims_plot.jpg")
knitr::include_graphics(load_path)

>>>>

load_path <- here::here("figures","SD_sensitivity_rev.jpg")
knitr::include_graphics(load_path)

@@

load_path <- here::here("figures","compatibility_plot_rev.jpg")
knitr::include_graphics(load_path)

@@

load_path <- here::here("figures","simultaneous_sims_plot_rev.jpg")
knitr::include_graphics(load_path)
